---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rearcut)](https://cran.r-project.org/package=rearcut)
[![Travis-CI Build Status](http://badges.herokuapp.com/travis/hypertidy/rearcut?branch=master&env=BUILD_NAME=trusty_release&label=linux)](https://travis-ci.org/hypertidy/rearcut)
[![Build Status](http://badges.herokuapp.com/travis/hypertidy/rearcut?branch=master&env=BUILD_NAME=osx_release&label=osx)](https://travis-ci.org/hypertidy/rearcut) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hypertidy/rearcut?branch=master&svg=true)](https://ci.appveyor.com/project/hypertidy/rearcut) 
[![Coverage status](https://codecov.io/gh/hypertidy/rearcut/branch/master/graph/badge.svg)](https://codecov.io/github/hypertidy/rearcut?branch=master)


# rearcut

The goal of rearcut is to triangulate polygons using the [Ear clipping algorithm](https://en.wikipedia.org/wiki/Polygon_triangulation#Ear_clipping_method). This is also referred to as [ear cutting](http://cgm.cs.mcgill.ca/~godfried/teaching/cg-projects/97/Ian/cutting_ears.html) and this package directly uses the [Mapbox Javascript library earcut](https://github.com/mapbox/earcut).

The original motivation for rearcut is to triangulate polygons for [silicate](https://github.com/hypertidy/silicate.git). 


A polygon and one of its possible triangulations by ear clipping. 

```{r}

```
[silicate](https://github.com/hypertidy/silicate.git). 

The basic function `earcut` for generic data is to be called with x/y coordinates in `x` (using the `grDevices::xy.coords` conventions) and an optional marker index of where holes are. 

```{r}
## example data from polypath
## rather than separate rings by NA we indicate those positions
## (here the hole starts at 5 and is the only one)
x <- c(.1, .1, .9, .9, .2, .2, .8, .8)
y <- c(.1, .9, .9, .1, .2, .8, .8, .2)
library(rearcut)
ind <- earcut(cbind(x, y), holes = 5L)
rearcut:::plot_tri(x, y, ind, col = "grey")
```

The idea is that more specialist contexts will wrap this lower level. 

Another example. 

```{r}
txt <- readLines("https://raw.githubusercontent.com/mapbox/earcut/master/test/fixtures/water-huge.json")
library(dplyr)
x <- jsonlite::fromJSON(txt) %>% purrr::map_df(tibble::as_tibble, .id = "poly")


x <- x %>% filter(poly == 1)
tri <- earcut(x[c("V1", "V2")])
rearcut:::plot_tri(x$V1, x$V2, tri)
```

## Installation

Rearcut may be installed from Github. 

```{r,eval=FALSE}
## install.packages("devtools")
devtools::install_github("hypertidy/rearcut")
```


Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
  
  
